Prestige bias in cultural evolutionary dynamics

### 2023-03-09 ms/ms.tex
added todos from MWF

To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
This is an important distinction, as influence is a context-{dependent} bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that {have} already copied each role-model, which may be easier and more accurate to estimate {than} success. 
Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.

@@

We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, {propose} an extension with influence bias, and then develop a model with a dichotomous trait.
We {implement} our stochastic models and approximations, {perform} statistical analyses, and {produce} figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

\subsection*{Continuous trait}
We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
{Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait. Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t${, and}  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
Cultural transmission is modeled by a function $F$ such that 
\begin{equation}\label{eq:transmission}
A_{i}(t+1) = F_i(\vec{A}(t)) \;.
\end{equation}

\paragraph{Success bias.}
{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$,  a weighted average of the traits of all role-models, {as}
\begin{equation}\label{eq:boydF}
F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{i,j} \;, 
\end{equation}
where $G_{i,j}$ is the success bias of role-model $j$ in the eyes of copier $i$,
\begin{equation}\label{eq:boydG}
G_{i,j} = \frac{\beta(A_{i,j})}{\sum_{k=1}^{N} \beta(A_{i,k})} \;,
\end{equation}
$A_{i,j}$ is the absolute trait value {that} copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
\begin{equation}\label{eq:relativeTrait}
A_{i,j} = A_j + e_i,
\end{equation}
and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model,
\begin{equation}\label{eq:success_bias}
\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)} \;,
\end{equation} 
with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength.
Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$.

@@

Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs. influence in the role-model's overall prestige in the eyes of the copier.

@@

\subsection*{Dichotomous trait}
{We} introduce a simplified version where the trait {has only} two phenotypes: {an} optimal phenotype $\hat{A}$ and {a} sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability {that} that phenotype {is} transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, {which entails} exchangeability between role-models.
Therefore, the probability {that} the $i$-th copier {copies} phenotype $A$ is
\begin{equation}\label{eq:binary-model}
G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$, $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, $\beta(\hat{A})=1$, and $\alpha'= \frac{\alpha}{1-\alpha}$ is the {odds} ratio of the bias weight. Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
The rest of the details follow the continuous trait model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
Our model is defined by two nested stochastic processes. Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two such approximations, summarized here and explained in detail below. In both we assume either $\alpha_j$ is a trait of role-model $j$ only ({different from} $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.

@@

\paragraph{Dirichlet-Multinomial approximation.}
The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.

Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.

@@

\begin{proof}
{Let} $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ {be} the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ {out} of $i-1$ copiers chose role-model $j$. 
Using conditional probability and \cref{eq:recurrence},
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1) \;,
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
\Cref{recursive} is equivalent to eq.~(2.1) by \citep{GBD}, which completes the proof.
\end{proof}
This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process. The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
\\

@@

\begin{proof}
{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that 
$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
\end{proof}

\begin{corollary}\label{cor:GBD}
$\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
\end{corollary}

@@

\paragraph{Numerical validation.}
To validate our results we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}.

@@

{Frigyik et al.}\ \citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

@@

\paragraph{Numerical validation.}
To validate our analytical result (\Cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
First, we {compute} an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
We then {compare} this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A). The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead. The maximum difference is 0.5 role-models, which {indicates} a very good fit.
In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B). We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, {strongly} supporting our approximation.

Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
{That} the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
We examined the robustness of the DM approximation to relaxing the approximation assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $q \in [10^{-7},10^{-1}]$. 
We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}

After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
For simplicity, we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).

@@

\begin{result}[Drift and diffusion terms in a constant environment]
Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
Then,
\begin{equation}
E[x'-x] \approx x(1-x)(1-\beta) \;, 
\quad
V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
\end{equation} 
\end{result}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
  The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
  Fixation probability (A) is bounded by $2(1-\beta)$ (blue).
  Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (A and B), $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); success coefficient, $1-\beta=s=0.044$ (A and B); success-bias weight, $\alpha=0.01$ (panels C and D).}
  \label{fig:var_alpha}
\end{figure}

@@

\begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
Let $x$ be the initial frequency of the invading phenotype and $X_t$ {the} number of individuals with {that} phenotype after $n$ generation.
Then,
\begin{equation}\label{eq:ch_expected_and_var}
E[X_n/N - x] \simeq x(1-x) S_n / N_e \;, 
\quad
\text{and}
\quad
V(X_n/N-x) \simeq  n x(1-x) / N_e \;,
\end{equation}
where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$.
\end{result}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (A, C, and D) and 95\% (B) confidence intervals.
  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$ (A and B), $A=0.8$ (C and D); In (A), the success coefficient is: $1-\beta=s=0.005$; In (B, C, and D) the success-bias weight is $\alpha=0.1$.}
  \label{fig:ch_env_alpha_beta}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Adaptive success-bias weight}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
%During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
{Some} cultural traits or cultural role-models may be copied more often {than others} due to transmission biases. 
{One such} bias is success bias, in which copiers are more likely to copy a successful role-model. {Although many} models assume that success can be accurately estimated{, it} has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
This perceived success can be determined by performance {with respect to another trait (indirect)} \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.

>>>>

To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
This is an important distinction, as influence is a context-{dependent} bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that {have} already copied each role-model, which may be easier and more accurate to estimate {than} success. 
Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying. % TODO check this - is influence frequency dependent?

@@

We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
We implement our stochastic models and approximations, {perform} statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

\subsection*{Continuous trait}
We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. % TODO If you omit the indirect trait, it is no longer indirect transmission.
{Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
% We need to mention that each copier chooses one role model out of the entire population; this is different from other models studied by Feldman and colleagues in which the population is infinite and each copier samples n role models, and uses those n role models to determine its trait:
%  Denton, Kaleda K, Yoav Ram, and Marcus W. Feldman. 2023. “Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872). https://doi.org/10.1098/rstb.2021.0400.
% Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W. Feldman. 2020. “Cultural Evolution of Conformity and Anticonformity.” Proceedings of the National Academy of Sciences 117 (24): 13603–14. https://doi.org/10.1073/pnas.2004102117.
% Boyd & Richerson book
Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t${, and}  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
Cultural transmission is modeled by a function $F$ such that 
\begin{equation}\label{eq:transmission}
A_{i}(t+1) = F_i(\vec{A}(t)) \;.
\end{equation}

\paragraph{Success bias.}
{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a  transmission algorithm by defining $F$, a weighted average of the traits of all role-models, as
\begin{equation}\label{eq:boydF}
F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{i,j} \;, 
\end{equation}
where $G_{i,j}$ is the success bias of role-model $j$ in the eyes of copier $i$,
\begin{equation}\label{eq:boydG}
G_{i,j} = \frac{\beta(A_{i,j})}{\sum_{k=1}^{N} \beta(A_{i,k})} \;,
\end{equation}
$A_{i,j}$ is the absolute trait value {that} copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
\begin{equation}\label{eq:relativeTrait}
A_{i,j} = A_j + e_i,
\end{equation}
and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model \citep[eq.~5.11]{evolutionBook},
\begin{equation}\label{eq:success_bias}
\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)} \;,
\end{equation} 
with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength.
Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$.

@@

Here, the bias weight $\alpha_{ij}$ determines the relative weighting of success and influence bias. It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs. influence in the role-model's overall prestige in the eyes of the copier.

@@

\subsection*{Dichotomous trait}
{We} introduce a simplified version where the trait {has only} two phenotypes: {an} optimal phenotype $\hat{A}$ and {a} sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability {that} that phenotype {is} transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, {which entails} exchangeability between role-models.
Therefore, the probability {that} the $i$-th copier {copies} phenotype $A$ is
\begin{equation}\label{eq:binary-model}
G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$; $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model; assuming (without loss of generality) that $\beta(\hat{A})=1$; and defining $\alpha'= \frac{\alpha}{1-\alpha}$ as the odds ratio of the bias weight.
Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
The rest of the details follow the continuous trait model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
Our models are defined by two nested stochastic processes. Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$, see \cref{eq:transmission}. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$, see \cref{eq:process}.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$, where $K_{N,j}$ is the number of copiers that chose role-model $j$ after all copiers chose a role model.
However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
In both we assume that the bias weight is completely homogeneous, $\alpha_{i,j}=\alpha$ (it is also enough to assume that $\alpha_j$ is a bias of role-model $j$ only, that is, it does not vary between copiers). % TODO but result 1 has alpha_i
Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.

@@

\paragraph{Dirichlet-Multinomial approximation.}
The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning that the order of copiers does not matter.

@@

\begin{proof}
{Let} $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ {be} the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ {out} of $i-1$ copiers chose role-model $j$. 
Using conditional probability and \cref{eq:recurrence},
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1) \;,
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
\Cref{recursive} is equivalent to eq.~(2.1) by \citep{GBD}, which completes the proof.
\end{proof}
This result gives the following two corollaries on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$. The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
\\

@@

\begin{proof}
{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that 
$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). % TODO what is E[k]?
$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
\end{proof}

\begin{corollary}\label{cor:GBD} % TODO merge with the previous corollary
$\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
\end{corollary}

@@

\paragraph{Numerical validation.}
To validate our results  % TODO be more explicit - what exactly are you validating?
we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}. % TODO what are drift errors? not clear.

@@

Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, % TODO is the "number of draws" equal to our parameter N?  if so, did we check the sensitivity of this approximation to small N?
based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

@@

\paragraph{Numerical validation.}
To validate our analytical result (\Cref{cor:dirichlet}) % TODO again be more explicit what it is you are validating
and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model. % Also not clear what is the "full model" - ref to equation, and explain - you are comparing the DM approximation (result 2? corollary 3? eq 16? what?) to results of simulations of the model (not full), eq 10?
First, we compute an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
We then {compare} this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A). The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead. The maximum difference is 0.5 role-models, which {indicates} a very good fit.
In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B). We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, {strongly} supporting our approximation.

Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
That the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
We examined the robustness of the DM approximation to relaxing the approximation assumptions. % TODO which assumptions? those given in result 2? if so, refer to them directly and repeat them (e=ej, alpha=alpha_j).
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance). % TODO Not clear what “varying scale (variance)” means
Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $q \in [10^{-7},10^{-1}]$. 
We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}
% TODO check that is its clear we are using the dichotomous model here
After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
For simplicity, we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).

@@

% TODO I'm not sure this needs to be a "Results" - I think we can write it here as apart of the analysis, which gives Result 4. Also, where is the actual proof of the equation in this result?
\begin{result}[Drift and diffusion terms in a constant environment]
Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
% TODO can we say beta=beta(A)/beta(hat A) ? then we dont force beta(hat A)=1
Then,
\begin{equation} % TODO remove \approx and instead add big-O notation
E[x'-x] \approx x(1-x)(1-\beta) \;, 
\quad
V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
\end{equation} 
\end{result}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{kimura_var.pdf}
  \caption{\textbf{Fixation probability and time in a constant environment.}
  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
  The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
  Fixation probability (A) is bounded by $2(1-\beta)$ (blue).
  Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (panels A and B), 
   $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); % TODO this is not clear
   success coefficient, $1-\beta=s=0.044$ (panels A and B); 
   success-bias weight, $\alpha=0.01$ (panels C and D).
   }
  \label{fig:var_alpha}
\end{figure}

@@

\begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
Let $x$ be the initial frequency of the invading phenotype and $X_t$ {the} number of individuals with {that} phenotype after $n$ generation.
Then,
\begin{equation}\label{eq:ch_expected_and_var}
E[X_n/N - x] \simeq x(1-x) S_n / N_e \;, 
\quad
\text{and}
\quad
V(X_n/N-x) \simeq  n x(1-x) / N_e \;,
\end{equation}
where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$. % TODO beta_t is note defined - maybe in the appendix? needs. to be defined above, before the reference to the appendix
\end{result}

@@

\begin{figure}[H]
    \includegraphics[width=\linewidth]{ch_env.pdf}
  \caption{\textbf{Fixation probability in a changing environment.}
\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis). The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange). 
\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
When success bias is large ($1-\beta > 0.1$),  
simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}). With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias. 
When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
  }
  \label{fig:ch_env_alpha_beta}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO MWF thinks the paper is better without this paragraph; if we remove, we should also remove references to it from abstac/intro/discussion
\subsection*{Adaptive success-bias weight}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
%During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
{Some} cultural traits or cultural role-models may be copied more often {than others} due to transmission biases. 
{One such} bias is success bias, in which copiers are more likely to copy a successful role-model. {Although many} models assume that success can be accurately estimated{, it} has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
This perceived success can be determined by performance with respect to another trait (indirect) \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
